%%Designed for IEEE Transactions on Vehicular Technology, based on bare_jrnl.tex by Michael Shell.
%%December. 2015
%%Length Requirements: The complete manuscript  should be prepared in final IEEE typesetting with maximum page length limited to 15 pages for a Regular Paper and 5 pages  for a Correspondence. 
%%Contact Info: admin-tvt@ece.ufl.edu
%%Designed by TVT editorial office


\documentclass[journal,10pt]{IEEEtran}



\begin{document}

\title{Template for IEEE TVT \LaTeX\ Submission}


\author{Yuguang ``Michael'' Fang,~\IEEEmembership{Fellow,~IEEE}

\thanks{Y. Fang is with the Department of Electrical and Computer Engineering, University of Florida, Gainesville, FL, 32611, USA e-mail: (see http://winet.ece.ufl.edu/tvt/ for further information regarding IEEE TVT.)}% <-this % stops a space
\thanks{Manuscript received XXX, XX, 2015; revised XXX, XX, 2015.}}

\markboth{IEEE Transactions on Vehicular Technology,~Vol.~XX, No.~XX, XXX~2015}
{}
%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}







\maketitle


\begin{abstract}
The abstract goes here.
\end{abstract}


\begin{IEEEkeywords}
Keywords goes here.
\end{IEEEkeywords}


\IEEEpeerreviewmaketitle



\section{Introduction}

This file is intended to serve as a template for IEEE Transactions on Vehicular Technology manuscripts under \LaTeX\ IEEEtran.cls version 1.8a and later.


\hfill August 4, 2015

\subsection{Subsection Heading Here}
Subsection text here.



\subsubsection{Subsubsection Heading Here}
Subsubsection text here.


\section{Proposed Scheme}
Scheme description goes here \cite{IEEEhowto:kopka}.



\section{Conclusion}
The conclusion goes here.


\appendices
\section{Proof of the ...}
Appendix one text goes here.


\section{}
Appendix two text goes here.



\section*{Acknowledgment}


The authors would like to thank...



\ifCLASSOPTIONcaptionsoff
  \newpage
\fi


\begin{thebibliography}{1}
% You can use other form of bib file by changing here... 

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}



\begin{IEEEbiography}{Yuguang ``Michael'' Fang}
Biography text here.
\end{IEEEbiography}

%It is not necessary to upload the biography when you submit your manuscript.


\end{document}


